Exploring Feature Engineering

### 2019-04-05 Scripts/evaluating_correlations.Rmd
added to correlation script

>>>>

#### Specific correlations

##### GM12878

######10kb

```{r}
cl = "GM12878"; resolution = "10kb";

vars1 <- c("02WeakPromoter", "06WeakEnhancer", "H2az", "H3k4me2", "H3k4me3", "H3k27ac", "H3k9ac", "DNase", "Runx3sc101553", "11WeakTxn", "07WeakEnhancer", "H3k4me1")

vars2 <- c("08Insulator", "Ctcf", "Ctcfsc15914c20", "Rad21", "Smc3ab9263", "Yy1sc281", "Znf143166181ap")

corrdata1 <- corrdata[which(rownames(corrdata) %in% vars1), which(colnames(corrdata) %in% vars1)]
colnames(corrdata1) <- rownames(corrdata1) <- colnames(corrdata1)[c(1,2,11,10,8,3,6,12,4,5,7,9)]

corrplot(corrdata1,
         method="number",
         type="upper", 
         #order="hclust", 
         tl.col="black", 
         #tl.srt=90,
         #tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

corrdata2 <- corrdata[which(rownames(corrdata) %in% vars2), which(colnames(corrdata) %in% vars2)]
colnames(corrdata2) <- rownames(corrdata2) <- colnames(corrdata2)[c(1,2,3,4,5,6,7)]

corrplot(corrdata2,
         method="number",
         type="upper", 
         #order="hclust", 
         tl.col="black", 
         #tl.srt=90,
         #tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))
```

##### K562

######10kb

```{r}
cl = "K562"; resolution = "10kb";

vars1 <- c("Ctcflsc98982", "Rad21", "Ctcfb", "Ctcf", "Ctcfc", "Smc3ab9263", "Znf143", "Cebpb")

vars2 <- c("Corestsc30189", "Mazab85725", "DNase", "H3k4me1", "H3k4me2", "H3k4me3", "Egr1", "Elf1sc631", "Zbtb7asc34508", "E2f6", "Max", "H2az", "02WeakPromoter", "06WeakEnhancer")

corrdata1 <- corrdata[which(rownames(corrdata) %in% vars1), which(colnames(corrdata) %in% vars1)]
colnames(corrdata1) <- rownames(corrdata1) <- colnames(corrdata1)[c(4,7,3,6,2,8,1,5)]

corrplot(corrdata1,
         method="number",
         type="lower", 
         #order="hclust", 
         tl.col="black", 
         #tl.srt=90,
         #tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

corrdata2 <- corrdata[which(rownames(corrdata) %in% vars2), which(colnames(corrdata) %in% vars2)]
colnames(corrdata2) <- rownames(corrdata2) <- colnames(corrdata2)[c(3,13,4,9:11,6,7,14,5,12,8,1,2)]

corrplot(corrdata2,
         method="number",
         type="lower", 
         #order="hclust", 
         tl.col="black", 
         #tl.srt=90,
         #tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))
```
